Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-07 ms.tex
Reach dust temperature ranges

% mention that the two different emissivity power laws allow 
% the model to simultaneously explain narrow SED peak, and flattening
% of SED toward the millimeter
At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
MBBs, one representing a `hot' grain population ($T$$\approx$), the other a 
`cold' grain population ($T$$\approx$).

>>>>

% mention that the two different emissivity power laws allow 
% the model to simultaneously explain narrow SED peak, and flattening
% of SED toward the millimeter
At sufficiently high frequencies, Galactic thermal dust emission can be 
adequately modeled as a single MBB with power-law emissivity 
\citep[e.g. SFD;][]{planckdust}. However, it has long been recognized, 
particularly in view of the FIRAS spectra, that the dust SED flattens toward 
the millimeter in a manner which is not consistent with a simple extrapolation 
of the single-MBB model to low frequencies. In the diffuse ISM, \cite{reach95} 
found an improved fit to the FIRAS data using a superposition of two $\beta$=2 
MBBs, one representing a `hot' grain population ($T$$\approx$16$-$21K), the 
other a `cold' grain population ($T$$\approx$4$-$7K).
